Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-20 manuscript/Chapter3-manuscript.Rmd
update ms intro ideas. update bib file

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success. Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions.

Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018]. Theory predicts that specialization through learning may result from past experiences in handling prey as well as a limited ability to retain complex learned skills for multiple prey types [@Tinker.etal2009]. Empirical studies shows that learning can optimize the efficiency of foraging strategies (e.g. search and handling times, return rates) potentially via associative images or increased reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015]. While this does not directly indicate foraging specialization, such optimization may reinforce the use of the same strategy (i.e. specialization) if its success is constant through repeated attempts. *parler des couts d'apprendre de quoi d'autre*

*expliquer comment ça optimise*
*expliquer comment ça peut mener aussi à de la plasticité*
*parler des coûts*

@@

@@

(travailler ceci) An important question that remains unanswered is how can generalist and specialist individuals coexist within predator populations. If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.

Several studies have shown that individual specialists can outperform

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn how to effectively use them is essential to maintain foraging success. Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions.

Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018]. Theory predicts that specialization through learning may be driven by past experiences as well as a limited ability to retain multiple complex hunting skills [@Tinker.etal2009]. Empirical studies show that learning enables predators to optimize the efficiency (e.g. search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015]. Such optimization may thus reinforce the use of the same tactic (i.e. specialization) if its success is constant through repeated attempts. *parler des couts d'apprendre de quoi d'autre*

*expliquer comment ça optimise*
*expliquer comment ça peut mener aussi à de la plasticité*
*parler des coûts*
*pt dire en haut que ça optimise directement et mène à la spécialisation*

@@

*un autre truc que je pourrais parler est le fait que si on assume que les individus deviennent meilleurs avec l'expertise (Dukas), on voit pourtant dans les études marines que les individus de groupes d'âges variés performent souvent de manière similaire. Ça amènerait bien l'autre paragraphe pour montrer que les interactions écologiques ont un rôle clé!!*

@@

(travailler ceci) An important question that remains unanswered is how can generalist and specialist individuals coexist within predator populations. If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components. Several studies have shown that individual specialists can outperform. *[ici je crois que je vais changer un peu cela. C'est surtout des idées. Ici on veut souligner l'importance des deux mais rappeler comme d'habitude que c'est difficile à mesurer à travers le temps blabla. J'introduis ensuite le jeu vidéo]*
